### 2021-03-06 chapters/sections/6-online_access_law.tex
überarbeitung

In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:
\begin{enumerate}
    \item \textbf{Digital availability of administrative services} \\
    An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.  As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.
    \item \textbf{Digital access to administrative services through administration portals of a portal network} \\
    Federal republic, each member state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}. 
    \item \textbf{Interoperable user profiles for accessing administrative services} \\
    Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.
\end{enumerate}

@@

\subsection{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services.

The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:

\paragraph{1. Create User Profile}
The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.

\paragraph{2. Login to User Profile}
Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal. The user has to finish authentication steps, which can consist for example of a username and password. Depending on the authentication method, a trust level of the current session is determined. With approval from the user, personal information from his profile is provided towards the form-server.

\paragraph{3. Selection of Administrative Service}
The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

\paragraph{4. Filling in Application}
Personal information from the user profile is used by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

\paragraph{5. Submission of Application}
The user again authenticates for his user profile and authorises the form-server to submit the application. The form-server saves the application until he is notified to delete it. The form-server submits the application to the administration portal which hosts the administrative service.

\paragraph{6. Reception of Application by Administration Portal}
The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.

\paragraph{7. Submission of Application to Data-Exchange Platform}
The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.

\paragraph{8. Management of Applications}
The administration portal stores active applications and enables the user to manage them.

\paragraph{9. Communication}
As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.  Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.

\subsection{System Architecture}
This subsection describes the system architecture of a member state relevant for the execution of the basic use case of the OZG based on the system architecture of Nordrhein-Westfalen. Systems responsible for coordination of OZG execution between member states and the federal republic are not the focus.

@@

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components. The most important components the service facade provides an interface for are:

\begin{itemize}
    \item \textbf{Responsibility Finder}

    This service component is used to find administrative institutions which are responsible for an application. Depending on the type of application and on the home address of the user, different institutions might be responsible.

    \item \textbf{Process Management}

    This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.

    \item \textbf{Search}

    This service component creates a list of URLs of administrative services relevant for a specified search term. This enables the portal to provide a search functionality of administrative services for the user.

    \item \textbf{User Profile Management}

    This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.

    \item \textbf{Application Management}

    This service component manages applications issued through the administration portal through communication with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

>>>>

This chapter gives an overview of regulations, execution and system architecture regarding the online access law.

\subsection{Regulations}

In 2017 the German government passed the law for improvement of online access to administrative services (Online Zugangs Gesetz: OZG) which requires federal republic and member states to execute the following regulations until 2022 \cite{BMI:OZG_Wortlaut}:

\paragraph{Digital availability of administrative services} An administrative service is the electronic processing of administrative procedures which are available from outside the governmental institution.  As it is not clear which administrative services exactly are meant by the definition of the OZG, the BMI created a catalogue \cite{BMI:Verwaltungsleistungen}. The OZG requires these services to be digitally available. As a guideline to what is considered sufficient availability, the BMI defined a maturity model \cite{BMI:Digitale_Services}.

\paragraph{Digital access to administrative services through administration portals of a portal network} Federal republic, each member state and each commune must provide an administration portal. Portals of communes must be linked to the portal of the corresponding member state. Portals of federal republic and member states must be connected through a portal network. \cite{BMI:Portalverbund} Each portal must provide a "seek and find" feature, which enables users to find all administrative services provided by any administration portal \cite{Cotar:Drucksache_19/19089}.

\paragraph{Interoperable user profiles for accessing administrative services} Federal republic and member states must provide user profiles which can be used to identify the corresponding person while requesting access to administrative services, to save personal information according to the once-only principle, to receive and send messages via a digital mailbox and to pay for services \cite{Cotar:Drucksache_19/19089}. The user profiles must be interoperable for every administration portal of the portal network.

\subsection{Execution}

@@

\subsection{System Architecture}
This subsection first describes the basic use case of the OZG. It then presents the OZG system architecture of a member state capable of executing the basic OZG use case.
Systems responsible for coordination of OZG execution between member states and the federal republic such as the online gateway are not included.

This section combines references from OZG system architectures from Baden-Würrtemberg \cite{ozg:bw} and Nordrhein-Westfalen \cite{ozg:nrw}.

\paragraph{Basic Use Case}
The BMI lists a total of almost 600 administrative services, each being described by a different process \cite{BMI:Informatiosplattform}. Each process consists of multiple sub-processes. When comparing the processes, one can see that some sub-processes occur very often and in similar arrangements. Those arrangements can be called the basic use case of OZG services. The basic use case describes the submission of an application for an administrative service and consists of the following arrangement of sub-processes \cite{NRW:Umsetzung}:

\begin{enumerate}
    \item \textbf{Create User Profile}

    The user creates a user profile on the administration portal of a member state by entering personal information and a authentication method like username and password or the German digital identity card.

    \item \textbf{Login to User Profile}

    Independent of the member state the user created the interoperable user profile for, he can use it in the current administration portal. The user has to finish authentication steps, which can consist for example of a username and password. Depending on the authentication method, a trust level of the current session is determined. With approval from the user, personal information from his profile is provided towards the form-server.

    \item \textbf{Selection of Administrative Service}

    The user visits any administration portal of the portal network and types a search term in the corresponding search field. The user is then presented with a list of search results consisting of administrative services. If the user selects a search result, he is forwarded to the correct page inside the domain of the administration portal which hosts the selected service. This page provides information about the administration service along with instructions on how to access the form for application. The interactive form, usually provided by a form-server, can be for example included in the page through a web-component.

    \item \textbf{Filling in Application}

    Personal information from the user profile is used by the form-server to fill as many fields of the form as possible. The form with prefilled information is then presented to the user. The interactive form can then be modified by the user. Depending on the form-server, additional functionalities like conditions between fields or sanity checking can be provided.

    \item \textbf{Submission of Application}

    The user again authenticates for his user profile and authorises the form-server to submit the application. The form-server saves the application until he is notified to delete it. The form-server submits the application to the administration portal which hosts the administrative service.

    \item \textbf{Reception of Application by Administration Portal}

    The administration portal receives the application from a form-server and usually just forwards it to the data-exchange platform and notifies the form-server that the he can delete the application.

    \item \textbf{Submission of Application to Data-Exchange Platform}

    The data-exchange platform distributes the application to the correct administrative institution responsible for processing it.

    \item \textbf{Management of Applications}

    The administration portal stores active applications and enables the user to manage them.

    \item \textbf{Communication}

    As part of an active application, the responsible institution can respond to the inbox of the user with status updates, requests or results.  Through the active application, he user can send messages to the responsible institution to request a status update or send additional information and documents.

@@

\paragraph{Administration Portal}
The administration portal is the component which directly interacts with users through a web site an provides the basic OZG use case through interaction with other system components. Through the web page of the portal, the user can create and manage his user profile, receive and send messages, upload and download documents, find administrative services, select an application form for an administrative service and be forwarded to the respective form server. Without direct visibility for the user, the portal also transmits personal information from the user profile to the form server, receives finished applications from the form server, determines responsible institutions and submits applications to the data exchange platform.
The administration portal consists of a web server, responsible for hosting web pages, and a facade for service components.

The service facade provides an interface to the \textbf{responsibility finder}. This service component is used to find administrative institutions which are responsible for an application. Depending on the type of application and on the home address of the user, different institutions might be responsible.

The service facade provides an interface to the \textbf{process manager}. This service component manages when the administration portal has to start which process in order to provide the basic OZG use case described earlier.

The service facade provides an interface to the \textbf{search service}. This service component creates a list of URLs of administrative services relevant for a specified search term. It enables the portal to provide a search functionality of administrative services for the user.

The service facade provides an interface to \textbf{user profile management}. This service component enables the administration portal to interact with the user profile component to retrieve JSON Web Tokens, update and read personal information and document wallet, to read messages of the inbox and send messages to an institution.

The service facade provides an interface to \textbf{application management}. This service component manages applications issued through the administration portal by communicating with the form server. The component enables the user to start an application by forwarding him to the correct form on the form server and optionally providing personal information to the form server. Form server and portal communicate about the status and content of the application. The user is able to keep track of the status of active applications through the profile, view their content, send messages to responsible institutions and cancel them.

### 2021-03-06 chapters/sections/7-messaging.tex
überarbeitung

\section{Messaging}

Messaging is an asynchronous system-to-system communication, delivering packages of data called messages trough channels. Messages can contain any structured data like strings, arrays or objects. It is up to the sender and receiver to determine and understand its content.

@@

During the routing of messages between systems, the content of messages might have to be modified. Therefore various message transformation components exist. Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message on a outbound channel.

@@

Depending on the messaging system solution, additional features can be configured to increase performance, stability, failure safety and more. If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently store messages in case of a system crash.

\section{Messaging Integration}

@@

The main benefit of messaging for integration is, that it enables systems to share services and data in a decoupled way. Neither system, whether sending or receiving messages, needs to be aware of each other.

@@

\section{Messaging Patterns}

@@

There exist different types of channels. In the thesis, named channels are publish-subscribe datatype channels. Unnamed channels are point-to-point channels. Publish-subscribe channels can be accessed by every system. In contrast to that, point-to-point channels can only be accessed by two systems - one writing and one reading system.

@@

Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system trough an API. The messaging adapter usually has to be developed for each system individually, and manually integrated into the code of the system trough asynchronous function calls of the adapter API.

@@

Message translators have the purpose of translating message content on data representation and data type layer.
On the data representation layer, message translators for example translate message content from an XML format to a JSON format. On the data type layer, message translators can for example concatenate first name and last name fields to a single name field.

@@

Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages, based on their content. The definition of the rules does not change during operation of the system.

Figure \ref{messaging:filter} shows the visual notation of a message filter.

@@

Content enricher have the purpose of adding new attributes to messages. The content which is added usually is a predetermined set of attributes but with dynamically created values.

@@

Message stores have the purpose of storing consumed messages in a database. They are also capable of communicating with other messaging patterns for providing access to stored messages. Communication between message patterns and message stores is indicated by a dotted arrows.

>>>>

\subsection{Messaging}

Messaging is an asynchronous system-to-system communication, delivering packages of data called messages through channels. Messages can contain any structured data like strings, arrays or objects. It is up to the sender and receiver to determine and understand its content.

@@

During the routing of messages between systems, the content of messages might have to be modified. Therefore various message transformation components exist. Their purpose is to consume messages from an inbound channel, modify their content based on predefined or dynamic rules and publish the modified message to an outbound channel.

@@

Depending on the messaging system solution, additional features can be configured to increase performance, stability, failure safety and more. If properly configured, the messaging system operates reliably, handles unreliable network connections and persistently stores messages in case of a system crash.

\subsection{Messaging Integration}

@@

The main benefit of messaging for integration is that it enables systems to share services and data in a decoupled way. Neither system, whether sending or receiving messages, needs to be aware of each other.

@@

\subsection{Messaging Patterns}

@@

There are different types of channels. In this thesis, named channels are publish-subscribe datatype channels. Unnamed channels are point-to-point channels. Publish-subscribe channels can be accessed by every system. In contrast to that, point-to-point channels can only be accessed by two systems - one writing and one reading system.

@@

Systems which do not natively support message based communication require a messaging adapter which enables the programs of the system to access the messaging system through an API. The messaging adapter usually has to be developed for each system individually, and manually integrated into the code of the system trough asynchronous function calls of the adapter API.

@@

Message translators have the purpose of translating message content on data representation and data type layer.
On the data representation layer, message translators translate message content for example from an XML format to a JSON format. On the data type layer, message translators can for example concatenate first name and last name fields to a single name field.

@@

Message filters contain a preconfigured set of filtering rules, which instruct the filter to delete messages based on their content. The definition of the rules does not change during operation of the system.

Figure \ref{messaging:filter1} shows the visual notation of a message filter.

@@

Content enricher have the purpose of adding new attributes to messages. The content which is usually added is a predetermined set of attributes but with dynamically created values.

@@

Message stores have the purpose of storing consumed messages in a database. They are also capable of communicating with other messaging patterns for providing access to stored messages. Communication between message patterns and message stores is indicated by a dotted arrow.

### 2021-03-06 chapters/sections/8-identity_management.tex
überarbeitung

@@

\paragraph{Usability}
Each service provider has different platform for management of personal information and identity related interactions. This can for example be web pages or applications for desktop and smartphone. Keeping track of all created user profiles is difficult. In case of web pages, users will also have to remember various URLs, usernames and passwords. The risk of forgetting login credentials is high. To manage personal information stored in each user profile and for example change an E-Mail address, users have to access the individual platforms of each service provider. Depending on the amount of created profiles, this can be a time consuming task. Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA or Magic-Link. Users receiving notifications, messages and mails on multiple platforms can quickly loose the overview and oversee important notifications. Each platform is often presented with a different design although the purpose remains similar. This makes it difficult for users to orientate themselves. Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while E-Mails are only used to notify the user to check his user profile ("You have unread messages!"). One reason is, that E-Mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content. Although service providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to. Service providers rely on the validity of information stored in the user profile. To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show his ID at a local shop. As each service provider manages separate user profiles, the user might have to go trough this time consuming process repeatedly. Users are not able to automatically share personal information from one user profile with another (except for some Single-Sign-On cases). As a result of that, creating new user profiles each time involves entering personal information all over again.

@@

\paragraph{Data Protection}
In the past, service providers established a habit of collecting more personal information than necessary for providing their services. As a response, the "Datenschutz Grundverordnung" - DSGVO (General Data Protection Regulation) was passed. Amongst other things, it requires service providers to inform the user about which personal information is processed, what the reason for processing the information is and how it is being processed. Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage. As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which service provider processes which personal information. Multiple service providers storing sensible information increases the risk of data being stolen due to a data breach.

In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also multiple systems operated by the member state. Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it. As a result of that, the administration portal has access to all personal information only the institution will eventually need to process. In addition, institutions actually do not require user profiles for processing applications. After an application is finished, the institution can delete all data stored as part of this process. The only reason user profiles are required is to verify the validity and authorization of incoming applications and to enable the user to comfortably fill in application forms and communicate trough an inbox.

@@

User profiles are often secured trough passwords. Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of it being stolen and all user profiles being accessible. With the amount of different service providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between service providers. Users also have to rely on the correct operation of the system architecture of the service provider and might not be able to proof failures in the operation of the system. If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proofing to the service provider, that he did cancel the subscription.

@@

The goal of IMP solutions is to replace user profiles with a single IMP identity. Trough the IMP client a user can manage his IMP identity and all integrated service providers. Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider. Depending on the use case, the relationship can be utilized differently. Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords. It also enables the user to update personal information shared with service providers trough one application. As the IMP client also contains an inbox, all notifications sent by each service provider can be viewed in the same place. As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can sent structured data to the IMP client along with the information that it should be displayed as a form. Depending on the content of the form and the use case of the service provider, the form can either be a purchase agreement or a survey. Assumed, trough a secure identification and validation process, the identity management provider makes sure, attributes users stores as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls. Due to the IMP client being able to automatically fill in attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.

@@

IMP puts the user back in control of his personal information. As part of the process of establishing a relationship, the service provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed. With this information, the user can make an informed decision whether to establish the relationship and the service provider performed his duty to inform the user as required by the DSGVO. As personal information is only shared as part of a relationship and with a specified purpose, the service provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible trough. This helps the service provider in processing personal information according to the DSGVO. As every relationship along with shared attributes is manageable trough the IMP client, the user wont loose track of which service provider has access to which personal information. The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the service provider processes only a small portion of attributes of IMP identities.

@@

The IMP client enables users to access their IMP identity and all relationships without the need of remembering a variety of credentials. This removes the risk of passwords being stolen. The IMP client itself can be secured without the need for a password. As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validate at any time. This enables both user and service provider to provide proof for interactions.

\section{IMP Integration Challenges}

In order for the system architecture of the OZG and service providers in general to utilize IMP services, the IMP connector has to be integrated. Multiple integration challenges are described in the following sections and will be focus of the integration architectures of chapter 4 and 5.

\paragraph{SP Challenges}

\begin{itemize}
    \item Sp does not understand concepts of the IMP like relationships, the integration has to bridge this gap
    \item The SP wants the integration to 
    \item Minimal modification of existing systems
    \item Maintainability
    \item Scalability
    \item Extendability
    \item Modularity
    \item

\end{itemize}

\paragraph{OZG Challenges}

\begin{itemize}
    \item Once an application is submitted, its attributes cannot be changed
    \item Mapping of IMP attributes and FIM data blocks
    \item 
\end{itemize}

\paragraph{IMP Challenges}

\begin{itemize}
    \item Connector has REST interface and cannot notify system architecture
    \item Connector does not understand messages
    \item API of connector can change
    \item New types of messages can be added by the client and the system provider might need to understand them
\end{itemize}

>>>>

This chapter describes issues of user based identity management in general and for the use case of the OZG. It also presents possibilities of how IMP can be utilized to solve mentioned issues.

@@

\paragraph{Usability}
Each service provider has a different platform for management of personal information and identity related interactions. This can for example be web pages or applications for desktop and smartphone. Keeping track of all created user profiles is difficult.

In case of web pages, users will also have to remember various URLs, usernames and passwords. The risk of forgetting login credentials is high.

To manage personal information stored in each user profile and for example change an e-mail address, users have to access the individual platforms of each service provider. Depending on the amount of created profiles, this can be a time consuming task. Especially if the user has to login to web pages using various authentication methods like passwords, single-sign-on, 2FA or Magic-Link. Users receiving notifications, messages and mails on multiple platforms can quickly loose track and oversee important notifications.

Each platform is often presented with a different design although the purpose remains similar. This makes it difficult for users to orientate themselves.

Bidirectional identity related interactions like subscribing for a service, canceling a subscription, sending or receiving a security relevant mail often only takes place trough a web page while e-mails are only used to notify the user to check his user profile ("You have unread messages!"). This is because e-mails do not provide a secure way of exchanging information and don't enable advanced interaction capabilities or exchange of structured content. Although service providers could develop mobile applications as an alternative for the web pages and benefit from secure communication and advanced interaction capabilities, due to the required investments many smaller SPs decide not to.

Service providers rely on the validity of information stored in the user profile. To guarantee that the information is correct, some SPs require users to take extra identification steps by for example performing a video call or requesting the user to show his ID at a local shop. As each service provider manages separate user profiles, the user might have to go trough this time consuming process repeatedly.

Users are not able to automatically share personal information from one user profile with another (except for some Single-Sign-On cases). As a result of that, creating new user profile each time involves entering personal information all over again.

@@

\paragraph{Data Protection}
In the past, service providers established a habit of collecting more personal information than necessary for providing their services. As a response, the "Datenschutz Grundverordnung" - DSGVO (General Data Protection Regulation) was passed. Amongst other things, it requires service providers to inform the user about which personal information is processed, what the reason for processing the information is and how it is being processed. Conventional user profile systems which store all personal information but do not differentiate between possibly different processing legitimisation of attributes increase the risk of illegitimate data usage.

As a result of the multitude of user profiles and the variety of platforms to manage them, users can quickly loose track of which service provider processes which personal information. Multiple service providers storing sensible information increases the risk of personal information being stolen due to a data breach.

In case of the OZG, the user shares personal information not only with institutions responsible for processing an application but also with multiple systems operated by the member state. Especially the administration portal used to initiate the application is problematic as it receives personal information from the interoperable user profile, sends it to a form server, eventually receives the filled in form and stores it. As a result of that, the administration portal has access to all personal information only the institution will eventually need to process. In addition, institutions actually do not require user profiles for processing applications. After an application is finished, the institution can delete all data stored as part of this process. The only reason user profiles are required is to verify the validity and authorization of incoming applications and to enable the user to comfortably fill in application forms and communicate through an inbox.

@@

User profiles are often secured through passwords. Especially in case of a large amount of profiles, users are tempted to use identical passwords, increasing the risk of it being stolen and all user profiles being accessible. With the amount of different service providers storing personal information and passwords, the risk of it being stolen increases as security of system architectures differs between service providers.

Users also have to rely on the correct operation of the system architecture of the service provider and might not be able to proof failures in the operation of the system. If for example the user cancels a subscription but the system architecture quietly fails to process it, the user might have issues proofing to the service provider, that he did cancel the subscription.

@@

The goal of IMP solutions is to replace user profiles with a single IMP identity. Through the IMP client a user can manage his IMP identity and all integrated service providers.

Instead of creating user profiles, the user can establish a relationship between his IMP identity and the service provider. Depending on the use case, the relationship can be utilized differently.

Using the IMP client, the user can keep track of all relationships without the need of remembering URLs, usernames or passwords.

It also enables the user to update personal information shared with service providers trough one application.

As the IMP client also contains an inbox, all notifications sent by each service provider can be viewed in the same place.

As part of established relationships, IMP client and service provider can securely exchange bidirectional structured data which along with advanced interaction capabilities of the IMP client can be used to create custom interaction scenarios: Service providers can send structured data to the IMP client along with the information that it should be displayed as a form. Depending on the content of the form and the use case of the service provider, the form can either be a purchase agreement or a survey.

Assumed, through a secure identification and validation process, the identity management provider makes sure, attributes users store as part of their IMP identity are correct, service providers wont require any additional identification steps trough for example video calls.

Due to the IMP client being able to automatically fill in attributes requested as part of a relationship, the user usually wont need to repeatedly manually enter personal information.

@@

IMP puts the user back in control of his personal information. As part of the process of establishing a relationship, the service provider has to specify exactly which attributes have to be shared, give a detailed explanation of why the attributes are required to be shared, what the purpose of the relationship is and how the attributes are processed. With this information, the user can make an informed decision whether to establish the relationship and the service provider performed his duty to inform the user as required by the DSGVO.

As personal information is only shared as part of a relationship and with a specified purpose, the service provider has an effective tool to differentiate processing legitimisation of attributes based on the type of relationship they are accessible trough. This helps the service provider in processing personal information according to the DSGVO.

As every relationship along with shared attributes is manageable trough the IMP client, the user wont loose track of which service provider has access to which personal information.

The risk of data being stolen decreases as most of the identity management and data storage is performed by the IMP system and the service provider processes only a small portion of attributes of IMP identities.

@@

The IMP client enables users to access their IMP identity and all relationships without the need of remembering a variety of credentials. This removes the risk of passwords being stolen. The IMP client itself can be secured without the need for a password. As the IMP system is capable of signing relationships and exchanged data, interactions between IMP identity and service provider can be validated at any time. This enables both user and service provider to provide proof for interactions.
